---
title: "p8105_hw1_cl4946"
output: github_document
---

```{r}

library(tidyverse)
data("penguins", package = "palmerpenguins")

```

### Q1
```{r}
penguins
names(penguins)
unique(penguins$species)
unique(penguins$island)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

The dataset contains `r nrow(penguins)` observations and `r ncol(penguins)` variables.
The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.
The `penguins` dataset contains data on Adelie, Chinstrap, and Gentoo penguins.
Important variables include `r names(penguins)`
The dataset contains `r nrow(penguins)` observations and
`r ncol(penguins)` variables. The mean flipper length is
`r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.


### Q2
```{r}
random_sample = rnorm(10)
random_sample > 0
character_vector = c(
  "a", "b", "c", "d", "e",
  "f", "g", "h", "i", "j"
)
factor_vector = factor(
  c(
    "low", "medium", "high", "low", "medium",
    "high", "low", "medium", "high", "low"
  )
)


```

