---
title: "p8105_hw1_cl4946"
output: github_document
---

```{r}

library(tidyverse)
data("penguins", package = "palmerpenguins")

```

### Q1
```{r}
penguins
names(penguins)
unique(penguins$species)
unique(penguins$island)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

The dataset contains `r nrow(penguins)` observations and `r ncol(penguins)` variables.
The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.
The `penguins` dataset contains data on Adelie, Chinstrap, and Gentoo penguins.
Important variables include `r names(penguins)`
The dataset contains `r nrow(penguins)` observations and
`r ncol(penguins)` variables. The mean flipper length is
`r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.


### Q2
```{r}
random_sample = rnorm(10)
random_sample > 0
character_vector = c(
  "a", "b", "c", "d", "e",
  "f", "g", "h", "i", "j"
)
factor_vector = factor(
  c(
    "low", "medium", "high", "low", "medium",
    "high", "low", "medium", "high", "low"
  )
)

problem2_df = tibble(
  random_sample = rnorm(10),
  positive = random_sample > 0,
  character_vector = c(
    "a", "b", "c", "d", "e",
    "f", "g", "h", "i", "j"
  ),
  factor_vector = factor(
    c(
      "low", "medium", "high", "low", "medium",
      "high", "low", "medium", "high", "low"
    )
  )
)



problem2_df


pull(problem2_df, random_sample)

mean(pull(problem2_df, random_sample))

mean(pull(problem2_df, positive))
mean(pull(problem2_df, character_vector))
mean(pull(problem2_df, factor_vector))
```
Taking the mean works for the numeric and logical variables, but does not work for the character or factor variables.

For the logical variable, R treats `TRUE` as 1 and `FALSE` as 0, so the mean corresponds to the proportion of `TRUE` values.

```{r}
as.numeric(pull(problem2_df, positive))
as.numeric(pull(problem2_df, character_vector))
as.numeric(pull(problem2_df, factor_vector))
```

Converting the logical variable to numeric produces 1 for `TRUE` and 0 for `FALSE`. Converting the character variable to numeric produces `NA` values because the character strings cannot be interpreted as numbers. Converting the factor variable to numeric returns the underlying integer codes for the factor levels rather than meaningful numeric values.

This helps explain why the mean works for the logical variable but not for
the character or factor variables.

